Quantifying the home ground advantage

### 2023-01-17 inst/home_advantage.Rmd
new ref
typo

We may apply `hyper3` idiom to the dataset. First a formal test:

@@

@@

Following lines create `home_advantage.rda`, residing in the `data/`
directory of the package.

>>>>

We may apply `hyper3` idiom to the dataset, using the likelihood
function of Davidson and Beaver (1977).  First a formal test:

@@

###  References

* R. R. Davidson and R. J. Beaver 1977. "On extending the
  Bradley-Terry model to incorporate within-pair order effects"
  _Biometrics_, 33:693--702

@@

Following lines create `baseball.rda`, residing in the `data/`
directory of the package.
